Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
wording

The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$, and $8$)  
leads to harder verification conditions to be checked 
by the {\sc verify} phase, which thus influences the overall synthesis time.   
However, considering the faster engine for each benchmark (marked as bold in Table~\ref{tab:results}), 
the median run-time amounts to $48$\,s, implying that \tool can synthesize 
half of the controllers in less than one minute. Overall, the average fastest synthesis 
time considering both engines is approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine, which is faster for two benchmarks where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2. 
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\ 
CBMC (SHA-1 hash) version: \\ 
7a6cec1dd0eb8843559591105235f1f2c4678801}

%--------------------------------------
\subsection{Threats to Validity and Generalizations}
%--------------------------------------

We have reported a favorable assessment of \tool over a diverse set of real-world
benchmarks. Nevertheless, this set of benchmarks is limited within the
scope of this paper and \tool's performance 
%may not generalize to other benchmark scenarios. This can 
needs to be addressed by expanding the benchmarks set
in future experiments.

>>>>

The presence of uncertainty in some particular benchmarks ($2$, $4$, $6$,
and $8$) leads to harder verification conditions to be checked by the {\sc
verify} phase, which impacts the overall synthesis time.  However,
considering the faster engine for each benchmark (marked in bold in
Table~\ref{tab:results}), the median run-time is $48$\,s, implying that
\tool can synthesize half of the controllers in less than one minute. 
Overall, the average fastest synthesis time considering both engines is
approximately $42$ minutes.  We consider these times short enough to be of
practical use to control engineers, and thus affirm RQ1.  We further observe
that the two-stage verification engine is able to synthesize stable
controllers for $19$ out of the $23$ benchmarks, and can be complemented
using the one-stage engine, which is faster for two benchmarks where the
inductive conjectures fail.  Both verification engines together enable
controller synthesis for $20$ out of $23$ benchmarks.  For the remaining
benchmarks our approach failed to synthesize a stable controller within the
time limits.  This can be addressed by either increasing either the time
limit or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers have been confirmed to be
stable outside of our model representation using MATLAB, positively
answering RQ2.  A~link to the full experimental environment, including
scripts to reproduce the results, all benchmarks and the \tool tool, is
provided in the
footnote.\footnote{\url{http://www.cprover.org/DSSynth/experiment.tar.gz}\\
CBMC (SHA-1 hash) version: \\ 7a6cec1dd0eb8843559591105235f1f2c4678801}

%--------------------------------------
\subsection{Threats to Validity}
%--------------------------------------

We have reported a favorable assessment of \tool over a diverse set of
real-world benchmarks.  Nevertheless, this set of benchmarks is limited
within the scope of this paper and \tool's performance needs to be assessed
on a larger benchmark set in future work.
